Hybrid platforms and bargaining

### 2023-04-19 src/presentation/topics_talk.qmd
Add bargaining equilibrium

::: {.fragment fragment-index=1}
 - Hybrid mode reduces fringe entry
$$
\small
\frac{\partial N_F^*}{\partial N_P} < 0
$$
:::
::: {.fragment fragment-index=2}
 - And, under certain conditions, total profits
$$
\small\text{Let } f(N_P, N_F) = g(\alpha N_P + \beta N_F)
$$
$$
\small\text{Then } \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}
$$
:::

@@

::: {.incremental}
 - Optimal entry fee is independent of $N_P$:
   $$ F_F^* = \sqrt{\mu I_F V_F} - I_F $$
 - Size of the aggregate is independent* of $N_P$:
   $$ A^* = \sqrt{\frac{\mu V_F}{I_F}} $$
 - Consumer welfare is also independent* of $N_P$:
   $$ CS^* \propto \log(A^*) $$
:::

>>>>

::: {.fragment fragment-index=1}
 - Hybrid mode reduces fringe entry
$$
\small
\frac{\partial N_F^*}{\partial N_P} < 0
$$
:::
::: {.fragment fragment-index=2}
 - And, under certain conditions, total profits: if $\small f(N_P, N_F) = g(\alpha N_P + \beta N_F)$ and $g'' < 0$
$$
\small\text{Then } \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}
$$
:::

@@

::: {.incremental}
 - Optimal entry fee is independent of $N_P$:
   $$ F_F^* = \sqrt{\mu I_F V_F} - I_F $$
 - Size of the aggregate is independent* of $N_P$:
   $$ A^* = \sqrt{\frac{\mu V_F}{I_F}} $$
 - **Consumer surplus** is also **independent*** of $N_P$:
   $$ CS^* \propto \log(A^*) $$
:::

## Bargaining equilibrium

::: {.incremental}
 - Total profits as a function of entrants have a simple form:
 $$
 f(N_P, N_F) = \mu \frac{n V_F + N_P V_P}{n V_F + N_P V_P + 1}
 $$
   - Satisfies the assumption for unique equilibrium
   - Has the form $f(N_P, N_F) = g(\alpha N_P + \beta N_F)$
   - $g$ is concave
 - Therefore,
 $$
 \frac{\partial N_F^*}{\partial N_P} < -\frac{V_P}{V_F}
 $$
:::

## Bargaining equilibrium

::: {.incremental}
 - Equilibrium aggregate and total profits are decreasing in $N_P$
 $$
 \frac{\partial A^*}{\partial N_P} < 0
 $$
   - Platform profits are increasing in $N_P$, though
 - **Consumer surplus** is also **decreasing** in $N_P$
 $$
 \frac{\partial CS^*}{\partial N_P} < 0
 $$
:::

## Results graphically
